### 2022-10-16 README.rmd
Correcting bug in issue #2
New version on cran

# geocmeans <img src='man/figures/geocmeans_logo.png' align="right" height="138.5" />
## An R package to perform Spatial Fuzzy C-means.

@@

>>>>

# geocmeans <img src='man/figures/geocmeans_logo.png' align="right" style = 'height:138px;'/>
## An R package to perform Spatial Fuzzy C-means.

@@

## Breaking news

Here we are! We are moving from `maptools`, `sp` and `rgeos` to `sf` and `tmap`. All the functions and the documentation were modified accordingly. If you spot an error or a bug, please open an issue on github.
